Comments on set up for application

### 2023-05-22 notes/application_K_choice.rmd
updates/corrections to thoughts r.e. choice of K

    \item I believe that this choice for $K_t$ likely yields an improper score. The basic reason is that the score depends on the value of the random variable/vector that is being forecasted and generally this is not allowed. A little more below.

@@

A few more thoughts about issues with propriety when setting $K_t = y^{tot}_t$:
\begin{enumerate}
\item Intuition:
    \begin{itemize}
    \item I think a slightly more careful (but still informal) definition of propriety than the informal one we usually use goes something like: in expectation, a proper scoring rule maximally rewards a forecast that corresponds to the conditional distribution of the random variable in question given all information available at the time $s$ that the forecast is produced.
    \item $y^{tot}_t$ was not observable at time $s$. A ``forecast" that knows $y^{tot}_t$ and conditions on that quantity in addition to other available information at time $s$ will be different (in general, probably narrower/more concentrated) than a forecast that conditions only on the information available at time $s$.
    \item Rephrasing the previous point: if I am omnipotent and I tell a forecaster, ``you will be scored using an allocation score using $K_t = 22,000$ because there will be 22,000 hospital admissions on the target date," I have leaked information about the future to that forecaster, and they will produce a forecast that differs from the forecast that would have been produced using only information available as of time $s$.
    \item In expectation, my score will likely reward the information-privileged forecaster more than the forecast corresponding to the conditional distribution of the random variable in question given all information available at time $s$. Therefore, it's not a proper score.
    \item The intuition in the above points is pretty rough.  I'd like to be able to state/prove this more precisely.
    \item I think the fact that we did this in our initial analysis and nobody immediately raised any red flags is a sign of how unclear all of this is. It feels kind of important that we say something about the fact that you can't do this in the manuscript, to warn readers/users off of this kind of analysis (assuming of course that I'm right about the resulting score being improper).
    \end{itemize}
\item More generally, for the integrated allocation score we probably need to pre-specify what the distribution over $K$ is. This makes perfect sense from the real-life perspective of a public health decision maker, it just gets tricky when you try to think about how to set up an evaluation exercise in an abstract setting without specific knowledge about $K$...
\item Rough start at an attempt to be a little more formal:
    \begin{itemize}
    \item Let $\mathcal{F}_s$ denote the sub $\sigma$-algebra generated by the collection $O_t$ of everything that's observable as of time $s$. Intuitively, this captures the set of all available information as of the time the forecast is generated.
    \item Let $\tilde{\mathcal{F}}_s$ denote the sub $\sigma$-algebra generated by $\tilde{O}_s = O_s \cup Y^{tot}_t$.  Noting that $Y^{tot}_t$ was not observable at time $s$, $\mathcal{F}_s \subset \tilde{\mathcal{F}}_s$.
    \item Maybe propriety is a statement about maximally rewarding the distribution of the random variable $Y_t$ given the sub $\sigma$ algebra $\mathcal{F}_s$, which is different from its distribution given $\tilde{\mathcal{F}}_s$? Where ``maximally rewarding" is in expectation with respect to... unclear \textemdash $\mathcal{F}_s$??
    \item I only half remember how this stuff works; will have to think a bit more to put the pieces together.
    \end{itemize}
\end{enumerate}

>>>>

    \item It's not clear to me whether or not this choice for $K_t$ likely yields an improper score. The basic reason is that the score depends on the value of the random variable/vector that is being forecasted. This may or may not be OK?

@@

\section{More on propriety}

Some general set up that's somewhere between Gerding et al. and Gneiting and Raftery:
\begin{itemize}
\item $(\mathcal{Y}, \mathcal{A})$ is a measurable space
\item $\mathcal{P}$ is a convex class of probability measures on $(\mathcal{Y}, \mathcal{A})$
\item A probabilistic forecast is any probability measure $F \in \mathcal{P}$
\item $S(F, y)$ is a scoring rule
\item $\overline{S}(F, G) = \mathbb{E}_{Y \sim G}[S(F, Y)]$ is the expected score for $F$ under the distribution $G$
\item The (negatively oriented) scoring rule $S$ is proper relative to $\mathcal{P}$ if $\overline{S}(G, G) \leq \overline{S}(F, G)$ whenever $F, G \in \mathcal{P}$
\item $s(x, y)$ is a loss function [or scoring function if $x$ is a functional of $F$]
\item We can obtain a scoring rule from a scoring function by setting $S(F, y) = s(x^F, y)$ where $x^F = \argmin_x \mathbb{E}_{Y \sim F} [s(x, Y)]$
\end{itemize}

Specifics for our set up for allocation:
\begin{itemize}
\item Our scoring function is $s_K(x,y) = \sum_{i=1}^n L (y_i - x_i)_+$ (subject to constraints that each $x_i$ is non-negative and $\sum_i x_i \leq K$, which I suppose we could build into $s_K$)
\item $x^F$ has entries $x^F_i = F_i^{-1}(1 - \lambda^{\star,F}(K) / L)$ where $\lambda^{\star,F}(K)$ is chosen such that $\sum_i x^F_i = K$
\item Our scoring rule is $S_K(F, y) = s_K(x^F, y) = \sum_{i=1}^n L (y_i - F_i^{-1}(1 - \lambda^{\star,F}(K) / L))_+$
\end{itemize}

Since $S_K$ is derived from a scoring rule using Bayes actions, it is a proper scoring rule. Writing this out a bit, we have to check that for all $F, G \in \mathcal{P}$:
\begin{align*}
&\overline{S}(G, G) \leq \overline{S}(F, G) \\
\Leftrightarrow \quad &\mathbb{E}_{Y \sim G}\left[ S_K(G, Y) \right] \leq \mathbb{E}_{Y \sim G}\left[ S_K(F, Y) \right] \\
\Leftrightarrow \quad &\mathbb{E}_{Y \sim G}\left[ \sum_{i=1}^n L (Y_i - G_i^{-1}(1 - \lambda^{\star,G}(K) / L))_+ \right] \leq \mathbb{E}_{Y \sim G}\left[ \sum_{i=1}^n L (Y_i - F_i^{-1}(1 - \lambda^{\star,F}(K) / L))_+ \right].
\end{align*}
But for any given $K$ this inequality holds by construction, because we chose the Bayes act allocation by minimizing the left hand side.

What about when $K = Y^{tot} = \sum_i Y_i$? Continuing from the last line above, we have
\begin{align*}
\quad &\mathbb{E}_{Y \sim G}\left[ \sum_{i=1}^n L (Y_i - G_i^{-1}(1 - \lambda^{\star,G}(Y^{tot}) / L))_+ \right] \leq \mathbb{E}_{Y \sim G}\left[ \sum_{i=1}^n L (Y_i - F_i^{-1}(1 - \lambda^{\star,F}(Y^{tot}) / L))_+ \right]
\end{align*}

I can't decide:
\begin{itemize}
\item Is the result now immediate through some kind of iterated expectations thing?
\item Or is this now complicated because $Y^{tot}$ (which is a function of all of the $Y_i$) appears in a nonlinear way in each of the terms of the summation, so that we can no longer separate into terms by location?
\end{itemize}
